|

### 2020-05-25 paper/Manuscript.Rmd
update 2020-05-25 19:44:33

The WORCS procedure and accompanying R-package provide a user-friendly and lightweight workflow for open, reproducible research in R, that meets all TOP-guidelines. It is beyond the scope of WORCS to support the incorporation of tools outside of the R-environment, or to containerize a project so that it can be identically reinstated on a different system or virtual machine. One important area of future development is to enable these extensions of the workflow. To this end, we are integrating WORCS into a modular framework of reproducibility tools for R [@repro]. This will make it possible for researchers to enhance a WORCS project with strict reproducibility tools like 'Docker' and 'Make', or vice versa, to initiate a WORCS project in a strictly reproducible environment. This combines the strengths of WORCS with those of @peikertReproducibleDataAnalysis2019.

>>>>

The WORCS procedure provides a user-friendly and
lightweight workflow for open, reproducible research, that meets all
TOP-guidelines. Nevertheless, there are clear directions for future developments.
Firstly, although the workflow is currently implemented only in R, it is 
conceptually relevant for users of other statistical programming languages, most
notably Python [@10.5555/1593511].
We welcome efforts to implement WORCS in other platforms.
Secondly, even when a project is in R, it may have dependencies outside of the
R environment that cannot be managed using `renv`.
It is beyond the scope of the `worcs` package to support the incorporation of
tools outside of R, or to containerize a project so that it can
be identically reinstated on a different system or virtual machine.
Therefore, another
important area of future development is to enable such extensions of the
workflow. To this end, we are collaborating with @repro on the development of
`repro`, an R-package that will facilitate setting up reproducibility tools such
as 'Make' and 'Docker'.
This will make it possible for researchers
to enhance a WORCS project with these strict reproducibility tools,
or vice versa, to initiate a WORCS project within a strictly reproducible
environment generated using `repro`. 
This will combine the strengths of the WORCS with those of the workflow proposed
by @peikertReproducibleDataAnalysis2019.
